---
title: "CW2"
author: "Isurika Bandara"
date: "2026-05-04"
output: html_document
---

```{r}
#Loading required package
library(dplyr)
library(ggplot2)
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
```

```{r}
#Loading the csv file.
data <- read.csv(file.choose(), header = TRUE)
```
```{r}
#Convert categorical variables to factors
data$gender <- as.factor(data$gender)
data$internet_access <- as.factor(data$internet_access)
```

```{r}
#removing missing values
data <- na.omit(data)
```
**objective 1**

**One-Sample T-Test**

To determine whether the average overall score of students is significantly different from the hypothesized value of 75.
```{r}
#Perform one-way ANOVA
t_test_one <- t.test(data$overall_score, mu = 75)
t_test_one

```
**Conclusion** **:** 
The average overall score is significantly different from 75 . The mean is significantly lower than 75.

# **objective 2**

**Independent T-Test**
To determine whether the overall score differs significantly between students with internet access 
```{r}
#one-sample t - test
t_test_two <- t.test(overall_score ~ internet_access, data = data)
t_test_two
```
**conclusion:**
The two-sample t-test shows no significant difference in overall scores between students with and without internet access. We fail to reject the null hypothesis.
# **objective 3**

**One-Way ANOVA**

To determine whether the overall score differs significantly among students with different stress levels.
```{r}
# Create stress level proxy using attendance percentage
data$stress_level <- cut(
  data$attendance_percentage,
  breaks = c(0, 60, 80, 100),
  labels = c("High Stress", "Medium Stress", "Low Stress")
)
anova_test <- aov(overall_score ~ stress_level, data = data)
summary(anova_test)
```
**conclusion:**  Students with varying attendance-based stress levels differ significantly in their overall academic performance . At least one stress group performs differently from others.